Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-07-08 ms.tex
adding optical depth at source for xinit plots

 \begin{figure}
    \centering
    \includegraphics{xinit_threepanel.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency.} 
    \label{fig:sol_mc_xinit}
\end{figure}

 \begin{figure}
    \centering
    \includegraphics{xinit_threepanel_tau1e6.pdf}
    \caption{Again shifting the initial photon frequency, but at a lower optical depth of $\tau_0 = 10^6$. The shift in $x$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the bias in the spectrum is much more drastic. } 
    \label{fig:sol_mc_xinit_lowtau}
\end{figure}

>>>>

 \begin{figure}
    \centering
    \includegraphics{xinit_threepanel.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency. The optical depth at each of these source frequencies is $\tau_s = 10^7, 77.2,$ and $18.6$, respectively.} 
    \label{fig:sol_mc_xinit}
\end{figure}

 \begin{figure}
    \centering
    \includegraphics{xinit_threepanel_tau1e6.pdf}
    \caption{Again shifting the initial photon frequency, but at a lower optical depth of $\tau_0 = 10^6$. The shift in $x$ is a much larger fraction of the distance to the spectral peak $(a\tau_0)^{1/3}$, and thus the bias in the spectrum is much more drastic. The optical depth at the source frequency is $\tau_s = 10^6$, $7.7$, and $1.9$ for $x_s=0.0, 6.0,$ and $12.0$, respectively. } 
    \label{fig:sol_mc_xinit_lowtau}
\end{figure}
